Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2023-02-06 manuscript.Rmd
fix labels
tau is also utf8

\begin{equation}
P(H|E) = \frac{P(H)P(E|H)}{P(E)} (\#eq:bayes)
\end{equation}

@@

\begin{equation}
P(E) = P(H)P(E|H) + P(\neg{}H)P(E|\neg{}H) (\#eq:total-expectedness)
\end{equation}

@@

\begin{equation}
\mathbb{E}(p(H|E)) = \int \frac{p(H)p(E|H)}{p(H)p(E|H)+p(\neg H) p(E|\neg H) } \; \text{d}\; \mathbb{P}(p(E|\neg H)) (\#eq:integral)
\end{equation}

@@

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Posterior Probability (corroboration as firmness) as a function of τ, where τ is either certain (solid line) or maximally uncertain (dotted line)."

@@

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Several measures for corroboration as increase in firmness as a function of τ, where τ is either certain (solid line) or maximally uncertain (dotted line)."

>>>>

\begin{equation}
P(H|E) = \frac{P(H)P(E|H)}{P(E)} \label{eq:bayes}
\end{equation}

@@

\begin{equation}
P(E) = P(H)P(E|H) + P(\neg{}H)P(E|\neg{}H) \label{eq:total-expectedness}
\end{equation}

@@

\begin{equation}
\mathbb{E}(p(H|E)) = \int \frac{p(H)p(E|H)}{p(H)p(E|H)+p(\neg H) p(E|\neg H) } \; \text{d}\; \mathbb{P}(p(E|\neg H)) \label{eq:integral}
\end{equation}

@@

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Posterior Probability (corroboration as firmness) as a function of $\tau$, where $\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Several measures for corroboration as increase in firmness as a function of $\tau$, where $\tau$ is either certain (solid line) or maximally uncertain (dotted line)."
